SMT-Boosted Security Types for Low-Level MPC

### 2025-11-07 toplas26/sty.tex
checkpoint

Both interactive and non-interactive judgements leverage the use
of SMT interpretations as described in Section \ref{section-smt}.
We introduce a \emph{share type} language $\sty$, classifying
\emph{share terms}. We represent share terms using standard notation
\cite{10.1007/978-3-030-68869-1_3}. A share term $[\phi_1,\phi_2]$
represents a secret-shared value where client 1 has $\phi_1$ and
client 2 has $\phi_2$, and this shared value can be reconstructed
as $\phi_1 + \phi_2$.\cnote{Comment on generation and
  reconstruction in general somewhere.} A share term $\pubx{\phi}$
denotes a publicly shared value.
$$
\begin{array}{rcl@{\hspace{10mm}}l}
  \sty &::=& \sharety \mid \pubty \mid \outty & \textit{share types} \\
  \stt &::=& [\phi,\phi] \mid \pubx{\phi} & \textit{share terms} 
\end{array}
$$

@@

@@

\begin{lemma}
  Assume given $\eqspre \wedge \toeq{\prog}, \Gamma,R: {OK}_\cid$  and
  $\iov(\prog) = S \cup V \cup O$
  and $\Gamma, \eqspre \wedge \toeq{\prog} \vdash [\phi_1,\phi_2] : \sharety$.
  Then, letting $X \defeq \ov(\Gamma) \cap \realviews{\setit{\cid_1}}{\setit{\cid_2}}$ for
  $\cid_1 \ne \cid_2$:
  $$
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}}  \cup X \cup \setit{\phi_1 + \phi_2}}
  = 
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}} \cup X \cup \setit{\phi_1 + \phi_2, \phi_1}}
  $$
\end{lemma}

@@

\begin{theorem}[Share Type Soundness]
  Assume given $\prog$ with 
  $\iov(\prog) = S \cup V \cup O$
  and $\eqspre \wedge \toeq{\prog} \vdash \varnothing,\varnothing \stredx^*
  \Gamma,R$ where $\realviews{\setit{\cid_1}}{\setit{\cid_2}} \cup O
  \subseteq \ov(\Gamma)$ for all $\cid_1$, $\cid_2$ with $\cid_1 \ne \cid_2$.
  Then $\prog$ satisfies noninterference modulo output.
\end{theorem}

>>>>

Both interactive and non-interactive judgements leverage the use
of SMT interpretations as described in Section \ref{section-smt}.
We introduce a \emph{share type} language $\sty$, classifying
\emph{share terms}. We represent share terms using standard notation
\cite{10.1007/978-3-030-68869-1_3}. A share term $[\phi_1,\phi_2]$
represents a secret-shared value where client 1 has $\phi_1$ and
client 2 has $\phi_2$, and this shared value can be reconstructed
as $\phi_1 + \phi_2$.\cnote{Comment on generation and
  reconstruction in general somewhere.} A share term $\pubx{\phi}$
denotes a publicly shared value.
$$
\begin{array}{rcl@{\hspace{10mm}}l}
  \sty &::=& \sharety \mid \pubty \mid \outty & \textit{share types} \\
  \stt &::=& [\phi,\phi] \mid \pubx{\phi} & \textit{share terms} 
\end{array}
$$ We proceed by formally describing the type analysis, then
discussing an illustrative example, and finally by demonstrating share
type soundness (Theorem \ref{theorem-sty}).

@@

Our non-interactive typing rules are presented in Figure
\ref{fig-stylocal}. Judgmements are of the form $\Gamma, \eqs \vdash
\stt : \sty$, where $\Gamma$ is a set of \emph{share type bindings} of
the form $\stt : \sty$. In the context of typing a protocol $\prog$
soundness requires that the constraint $\eqs$ must be entailed by
$\eqspre \wedge \toeq{\prog}$ (see, e.g., Lemma
\ref{lemma-sty-noninteractive-sound}).

The syntax-directed rules all known semi-homomorphic operations,
including addition of shares (\TirName{HEAdd}), and both addition and
multiplication of shares with a public value (\TirName{HEAddPub} and
\TirName{HEMultPub}, respectively) \cite{10.1007/978-3-030-68869-1_3}.
These rules also leverage SMT entailment in the \TirName{ShareEntails}
and \TirName{PubEntails} rules, since these operations should be
allowable up to algebraic equivalence in the context of a protocol.

@@

\begin{lemma}
  \label{lemma-sty-noninteractive-sound}
  Assume given $\eqspre \wedge \toeq{\prog}, \Gamma,R: {OK}_\cid$  and
  $\iov(\prog) = S \cup V \cup O$
  and $\Gamma, \eqspre \wedge \toeq{\prog} \vdash [\phi_1,\phi_2] : \sharety$.
  Then, letting $X \defeq \ov(\Gamma) \cap \realviews{\setit{\cid_1}}{\setit{\cid_2}}$ for
  $\cid_1 \ne \cid_2$:
  $$
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}}  \cup X \cup \setit{\phi_1 + \phi_2}}
  = 
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}} \cup X \cup \setit{\phi_1 + \phi_2, \phi_1}}
  $$
\end{lemma}

@@

\begin{theorem}[Share Type Soundness]
  \label{theorem-sty}
  Assume given $\prog$ with 
  $\iov(\prog) = S \cup V \cup O$
  and $\eqspre \wedge \toeq{\prog} \vdash \varnothing,\varnothing \stredx^*
  \Gamma,R$ where $\realviews{\setit{\cid_1}}{\setit{\cid_2}} \cup O
  \subseteq \ov(\Gamma)$ for all $\cid_1$, $\cid_2$ with $\cid_1 \ne \cid_2$.
  Then $\prog$ satisfies noninterference modulo output.
\end{theorem}
